---
title: "R-ASSIGNMENT-2"
author: "UDHAYA CHANDRU.M"
date: "11/3/2022"
output: html_document
---

## 1.Sort flights to find fastest flights

## ANSWER :

```{r}
  arrange(flights,arr_time)
```

## 2.Compare dep_time, sched_dep_time and dep_delay.How do you except those three numbers to be related?

## ANSWER :

```{r}
select(flights,dep_time,sched_dep_time,dep_delay)
```

1.  The scheduled departure time of the flights are the actual depature time of the flights.
2.  But some flights are depatured earlier or later than scheduled depature time.
3.  The Depature Delay of the flights are indicates earlier departure as NEGATIVE NUMBERS and later depature as POSITIVE NUMBERS in hours.

## 3.Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:

## a. A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time

## b. A flight is always 10 minutes late.

## c. A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.

## d. 99% of the time a flight is on time. 1% of the time it's 2 hours late

## ANSWER :

             According to the scenarios arr_delay is more important than dep_delay.

## 4.Which plane (tailnum) has the worst on-time record?

## ANSWER :

```{r}
arrange(flights,desc(dep_delay),desc(arr_delay))
```

## 5.Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.

## ANSWER :

## 1.

```{r}
select(flights,dep_time,dep_delay,arr_time,arr_delay)
```

## 2.

```{r}
select(flights,4,6,7,9)
```

## 3.

```{r}
select(flights,starts_with("dep_"),starts_with("arr_"))
```

## 4.

```{r}
select(flights,ends_with("_time"),ends_with("_delay"),-c(sched_arr_time,sched_dep_time,air_tim))
```
